X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2013-11-28 hedpc.tex
updated makefile

%\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
%% for review and submission
%\documentclass[aps,preprint,showpacs,superscriptaddress,groupedaddress]{revtex4}
% for double-spaced preprint
%\documentclass[aps,prl,floatfix,twocolumn,10pt]{revtex4-1}
%for review and submission
\documentclass[aps,prl,preprint,english]{revtex4-1} 
% for double-spaced preprint
%\documentclass[aip,apl,amsmath,amssymb,floatfix,preprint,a4paper]{revtex4-1}
%\documentclass[aip,apl,amsmath,amssymb,floatfix,reprint,a4paper]{revtex4-1}

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute
\usepackage{babel}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bf,small,labelsep=period]{caption}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}

\addto\captionsenglish{\renewcommand{\figurename}{Figure}}
%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\DeclareSIUnit{\voltpeak}{Vp}

%acronyms
\acrodef{CT}{computed tomography}
\acrodef{SNR}{signal-to-noise ratio}
\acrodef{CNR}{contrast-to-noise ratio}
\acrodef{SEM}{scanning electron microscope}
%% ----------------------------------------------------------------------------------------------------------------

@@

\author{T.~Thüring}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{M.~Abis}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}
\author{Z.~Wang}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\author{C.~David}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\author{M.~Stampanoni}
\affiliation{Paul Scherrer Institute, Villigen PSI, Switzerland}
\affiliation{Institute for Biomedical Engineering, Swiss Federal Institute of Technology, Zurich, Switzerland}

\date{\today}

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body of manuscript
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

X-ray radiography and \ac{CT} are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
diagnostic tasks in medicine. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering~\cite{Als-Nielsen2011}.

@@

Phase-sensitive
imaging is a desirable modality, as it delivers a complementary source of
contrast with respect to absorption by providing direct access 
to the electron density~\cite{Als-Nielsen2011}. Moreover, the combination with
attenuation enables the determination of the effective atomic
number~\cite{Qi2010}.
An enhanced
\ac{CNR} in images compared to attenuation for certain
materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
demonstrated.

@@

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013} and 
$\SI{123}{\kilo\electronvolt}$~\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require an acceleration voltage between \num{100} and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

@@

Our design introduces the edge-on
illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios. 
\begin{figure}[ht]
    \includegraphics[width=.7\textwidth]{figures/figure1.eps}
    \caption{Schematic of a grating
        interferometer for X-ray energies between 60 and
        \SI{150}{\kilo\electronvolt} in edge-on illumination mode. The
        aspect ratio is defined by the ratio of the travelling distance along the
        grating lines and the period and can be arbitrarily long. In order to maximise
        the field of view, the grating structures are aligned on an
    arc.}
    \label{Fig:schematic}
\end{figure}

@@

The combination of edge-on illumination and circularly aligned structures
enables phase-contrast imaging at arbitrary design energies and with a
maximum field of view in the horizontal direction ($x$ direction). These
advantages come at the expense of a limited field of view in the vertical
direction ($y$ direction), which is, depending on the X-ray detector,
typically a few pixels. 
However, radiographic 2D imaging can be obtained by scanning the sample or a thin fan
beam. The scanning technique has been demonstrated to deliver less dose than
the conventional approach based on the illumination of a large area. In
digital mammography, for instance, where dose is a critical issue, Philips'
MicroDose system combines a scanning approach with an highly collimated fan
beam~\cite{Aslund2007}. Thanks to the high collimation, the dose deposited
on  patients has been reported to be significantly lower than with other
instruments based on the illumination of a large area
detector~\cite{Oduko2010}.
Similarly, for tomographic images,
the approach allows single slice \ac{CT} or full 3D imaging in scanning mode.

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

\section*{Methods}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The \ac{SNR} is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~\SI{14}{\percent} already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the \ac{SEM} images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.

\bibliographystyle{apsrev4-1}
%\bibliography{library}

%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
%Control: key (0)
%Control: author (72) initials jnrlst
%Control: editor formatted (1) identically to author
%Control: production of article title (-1) disabled
%Control: page (0) single
%Control: year (1) truncated
%Control: production of eprint (0) enabled
\begin{thebibliography}{33}%
\makeatletter
\providecommand \@ifxundefined [1]{%
 \@ifx{#1\undefined}
}%
\providecommand \@ifnum [1]{%
 \ifnum #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \@ifx [1]{%
 \ifx #1\expandafter \@firstoftwo
 \else \expandafter \@secondoftwo
 \fi
}%
\providecommand \natexlab [1]{#1}%
\providecommand \enquote  [1]{``#1''}%
\providecommand \bibnamefont  [1]{#1}%
\providecommand \bibfnamefont [1]{#1}%
\providecommand \citenamefont [1]{#1}%
\providecommand \href@noop [0]{\@secondoftwo}%
\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
\providecommand \@href[1]{\@@startlink{#1}\@@href}%
\providecommand \@@href[1]{\endgroup#1\@@endlink}%
\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
\providecommand \@@startlink[1]{}%
\providecommand \@@endlink[0]{}%
\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
\providecommand \urlprefix  [0]{URL }%
\providecommand \Eprint [0]{\href }%
\providecommand \doibase [0]{http://dx.doi.org/}%
\providecommand \selectlanguage [0]{\@gobble}%
\providecommand \bibinfo  [0]{\@secondoftwo}%
\providecommand \bibfield  [0]{\@secondoftwo}%
\providecommand \translation [1]{[#1]}%
\providecommand \BibitemOpen [0]{}%
\providecommand \bibitemStop [0]{}%
\providecommand \bibitemNoStop [0]{.\EOS\space}%
\providecommand \EOS [0]{\spacefactor3000\relax}%
\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
\let\auto@bib@innerbib\@empty
%</preamble>
\bibitem [{\citenamefont {Als-Nielsen}\ and\ \citenamefont
  {McMorrow}(2011)}]{Als-Nielsen2011}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
  {Als-Nielsen}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
  {McMorrow}},\ }\href
  {http://books.google.com/books?hl=en\&lr=\&id=rlqlboWlTRMC\&oi=fnd\&pg=PA29\&dq=Elements+of+Modern+X-ray+Physics\&ots=P2D3XwrDgd\&sig=b3iO97q1hfsT8TkTYKxsvUbFink}
  {\emph {\bibinfo {title} {{Elements of modern X-ray physics}}}}\ (\bibinfo
  {year} {2011})\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Qi}\ \emph {et~al.}(2010)\citenamefont {Qi},
  \citenamefont {Zambelli}, \citenamefont {Bevins},\ and\ \citenamefont
  {Chen}}]{Qi2010}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
  {Qi}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zambelli}},
  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Bevins}}, \ and\ \bibinfo
  {author} {\bibfnamefont {G.-H.}\ \bibnamefont {Chen}},\ }\href {\doibase
  10.1088/0031-9155/55/9/016} {\bibfield  {journal} {\bibinfo  {journal}
  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {55}},\
  \bibinfo {pages} {2669} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2007)\citenamefont
  {Pfeiffer}, \citenamefont {Bunk}, \citenamefont {David}, \citenamefont
  {Bech}, \citenamefont {{Le Duc}}, \citenamefont {Bravin},\ and\ \citenamefont
  {Cloetens}}]{Pfeiffer2007a}%
  \BibitemOpen
  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}},
  \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {David}}, \bibinfo
  {author} {\bibfnamefont {M.}~\bibnamefont {Bech}}, \bibinfo {author}
  {\bibfnamefont {G.}~\bibnamefont {{Le Duc}}}, \bibinfo {author}
  {\bibfnamefont {A.}~\bibnamefont {Bravin}}, \ and\ \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Cloetens}},\ }\href {\doibase
  10.1088/0031-9155/52/23/010} {\bibfield  {journal} {\bibinfo  {journal}
  {Physics in medicine and biology}\ }\textbf {\bibinfo {volume} {52}},\
  \bibinfo {pages} {6923} (\bibinfo {year} {2007})}\BibitemShut {NoStop}%
\bibitem [{\citenamefont {McDonald}\ \emph {et~al.}(2009)\citenamefont

>>>>

\documentclass{pnastwo}

%% Packages
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{graphicx}  %figures
\usepackage[detect-all]{siunitx}
%\usepackage{pnastwof}

%% New commands
\newcommand{\msub}[1]{\ensuremath{\textnormal{\begin{tiny}#1\end{tiny}}}}
\renewcommand{\d}[1]{\ensuremath{\operatorname{d}\!{#1}}}
\DeclareSIUnit{\voltpeak}{Vp}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Don't type in anything in the following section:
%%%%%%%%%%%%
%% For PNAS Only:
\contributor{Submitted to Proceedings
of the National Academy of Sciences of the United States of America}
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%%%%%%%%%%%%

@@

\author{T.~Thüring
\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}
\affil{2}{Institute for Biomedical Engineering, Swiss Federal
Institute of Technology,
Gloriastrasse 35
8092 Zurich, Switzerland}}
\author{M.~Abis
\affil{1}{}
\affil{2}{}}
\author{Z.~Wang}
\affil{1}{}
\author{C.~David}
\affil{1}{}
\author{M.~Stampanoni
\affil{1}{}
\affil{2}{}}

\author{}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

%% The \maketitle command is necessary to build the title page.
\maketitle

\begin{article}

\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match the beam
    divergence and allow a large field of view on a short and efficient
    setup.
\end{abstract}

%% When adding keywords, separate each term with a straight line: |
\keywords{X-ray phase contrast | grating interferometry | X-ray interferometry}

%% Optional for entering abbreviations, separate the abbreviation from
%% its definition with a comma, separate each pair with a semicolon:
%% for example:
%% \abbreviations{SAM, self-assembled monolayer; OTS,
%% octadecyltrichlorosilane}

\abbreviations{
%acronyms
CT,computed tomography;
SNR,signal-to-noise ratio;
CNR,contrast-to-noise ratio;
SEM,scanning electron microscope;
}
%% ----------------------------------------------------------------------------------------------------------------
%% The first letter of the article should be drop cap: \dropcap{}
%\dropcap{I}n this article we study the evolution of ''almost-sharp'' fronts

\section{Significance statement}
Phase sensitive X-ray imaging provides access to additional information
on the investigated samples with respect to the conventional absorption
radiography and tomography.

Here we show a grating interferometer with a new design of the optical
elements that enables a large field of view and an efficient imaging at
a target energy of~\SI{100}{\kilo\eV} on a conventional tube.

Our results demonstrate that phase contrast can be achieved at these
energies, which are relevant for many applications, ranging from medical
diagnostics to nondestructive testing or homeland security.

\section{}
\dropcap{X}-ray radiography and CT are standard imaging techniques in
materials and life sciences for the nondestructive examination of samples or
diagnostic tasks in medicine. The underlying contrast mechanism
relies on the different X-ray attenuation properties of different materials
or tissue types. The dominant physical effects contributing to attenuation
are the photoelectric effect and incoherent (Compton) scattering. Besides attenuation, the wave
nature of X-rays reveals another contrast mechanism, which is the phase
shift. The interaction contributing to phase shifts is coherent (Rayleigh)
scattering~\cite{Als-Nielsen2011}.

@@

Phase-sensitive
imaging is a desirable modality, as it delivers a complementary source of
contrast with respect to absorption by providing direct access 
to the electron density~\cite{Als-Nielsen2011}. Moreover, the combination with
attenuation enables the determination of the effective atomic
number~\cite{Qi2010}.
An enhanced
CNR in images compared to attenuation for certain
materials or tissues~\cite{Pfeiffer2007a,McDonald2009} has also been
demonstrated.

@@

High-energy Talbot interferometry has been reported so far using a
synchrotron source at nominal energies of
$\SI{82}{\kilo\electronvolt}$~\cite{Willner2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied so far at $\SI{60}{\kilo\electronvolt}$ mean energy~\cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or CT require an acceleration voltage between \num{100} and
$\SI{150}{\kilo\voltpeak}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

@@

Our design introduces the edge-on
illuminated,  circularly aligned structures. Edge-on illumination
(Fig.~\ref{Fig:schematic}), as
opposed to face-on illumination, exploits the dimension along the grating
lines to form a high aspect ratio of the structures in the direction of the beam. The
effective structure height of the grating is then determined by the grating
dimension along the grating lines, which essentially allows arbitrarily high
aspect ratios.

@@

The combination of edge-on illumination and circularly aligned structures
enables phase-contrast imaging at arbitrary design energies and with a
maximum field of view in the horizontal direction ($x$ direction). These
advantages come at the expense of a limited field of view in the vertical
direction ($y$ direction), which is, depending on the X-ray detector,
typically a few pixels. 
However, radiographic 2D imaging can be obtained by scanning the sample or a thin fan
beam. The scanning technique has been demonstrated to deliver less dose than
the conventional approach based on the illumination of a large area. In
digital mammography, for instance, where dose is a critical issue, Philips'
MicroDose system combines a scanning approach with an highly collimated fan
beam~\cite{Aslund2007}. Thanks to the high collimation, the dose deposited
on  patients has been reported to be significantly lower than with other
instruments based on the illumination of a large area
detector~\cite{Oduko2010}.
Similarly, for tomographic images,
the approach allows single slice CT or full 3D imaging in scanning mode.

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can sufficiently attenuate X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.

@@

\section{Results and discussion}
Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependency of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.

@@

%% == end of paper:

%% Optional Materials and Methods Section
%% The Materials and Methods section header will be added automatically.

%% Enter any subheads and the Materials and Methods text below.
\begin{materials}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process~\cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

@@

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time was chosen in order to
get a low noise in the differential phase image. The SNR is
proportional to the visibility and the square root of the exposure
time~\cite{Raupach2011}.
This implies that the exposure times can easily drop by an order of
magnitude as these gratings become comparable in quality to those developed
in the last ten years. 
Smaller regions of these gratings actually exhibit a visibility up
to~\SI{14}{\percent} already, indicating that this goal is reachable as the
fabrication becomes more reliable and uniform.
\end{materials}

%% Optional Appendix or Appendices
%% \appendix Appendix text...
%% or, for appendix with title, use square brackets:
%% \appendix[Appendix Title]

\begin{acknowledgments}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the SEM images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
\end{acknowledgments}

%% PNAS does not support submission of supporting .tex files such as BibTeX.
%% Instead all references must be included in the article .tex document. 
%% If you currently use BibTeX, your bibliography is formed because the 
%% command \verb+\bibliography{}+ brings the <filename>.bbl file into your
%% .tex document. To conform to PNAS requirements, copy the reference listings
%% from your .bbl file and add them to the article .tex file, using the
%% bibliography environment described above.

%%  Contact pnas@nas.edu if you need assistance with your
%%  bibliography.

% Sample bibliography item in PNAS format:
%% \bibitem{in-text reference} comma-separated author names up to 5,
%% for more than 5 authors use first author last name et al. (year published)
%% article title  {\it Journal Name} volume #: start page-end page.
%% ie,
% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
% A short C-terminal sequence is necessary and sufficient for the
% targeting of chitinases to the plant vacuole. 
% {\it Proc Natl Acad Sci USA} 88:10362-10366.

%% Enter the largest bibliography number in the facing curly brackets
%% following \begin{thebibliography}

%\bibliographystyle{pnas}
%\bibliography{library}
\begin{thebibliography}{10}

\bibitem{Als-Nielsen2011}
Als-Nielsen J, McMorrow D (2011) {\em {Elements of modern X-ray physics}}.

\bibitem{Qi2010}
Qi Z, Zambelli J, Bevins N, Chen GH (2010) {Quantitative imaging of electron
  density and effective atomic number using phase contrast CT.}
\newblock {\em Physics in medicine and biology} 55:2669--77.

\bibitem{Pfeiffer2007a}
Pfeiffer F et~al. (2007) {High-resolution brain tumor visualization using
  three-dimensional x-ray phase contrast tomography.}
\newblock {\em Physics in medicine and biology} 52:6923--6930.

\bibitem{McDonald2009}
McDonald SA et~al. (2009) {Advanced phase-contrast imaging using a grating
  interferometer}.
\newblock {\em Journal of Synchrotron Radiation} 16:562--572.

\bibitem{Davis1995}
Davis T, Gao D, Gureyev T, Stevenson A, Wilkins S (1995) {Phase-contrast
  imaging of weakly absorbing materials using hard X-rays}.
\newblock {\em Nature} 373:595--598.

\bibitem{Chapman1997}
Chapman D et~al. (1997) {Diffraction enhanced x-ray imaging}.
\newblock {\em Physics in Medicine and Biology} 42:2015--2025.

\bibitem{Bonse1965}
Bonse U, Hart M (1965) {An x-ray interferometer}.
\newblock {\em Applied Physics Letters} 6:155--156.

\bibitem{Momose1996}
Momose A, Takeda T, Itai Y, Hirano K (1996) {Phase-contrast X-ray computed
  tomography for observing biological soft tissues}.
\newblock {\em Nature Medicine} 2:473--475.

\bibitem{Snigirev1995}
Snigirev A, Snigireva I, Kohn V, Kuznetsov S, Schelokov I (1995) {On the
  possibilities of x-ray phase contrast microimaging by coherent high-energy
  synchrotron radiation}.
\newblock {\em Review of Scientific Instruments} 66:5486--5492.

\bibitem{Wilkins1996}
Wilkins S, Gureyev T, Gao D, Pogany A, Stevenson A (1996) {Phase-contrast
  imaging using polychromatic hard X-rays}.
\newblock {\em Nature} 384:335--338.

\bibitem{Cloetens1996}
Cloetens P, Barrett R, Baruchel J, Guigay J, Schlenker M (1996) {Phase objects
  in synchrotron radiation hard x-ray imaging}.
\newblock {\em Journal of Physics D: Applied Physics} 29:133--146.

\bibitem{Cloetens1997}
Cloetens P, Guigay J, {De Martino} C, Baruchel J, Schlenker M (1997)
  {Fractional Talbot imaging of phase gratings with hard x rays.}
\newblock {\em Optics letters} 22:1059--61.

\bibitem{David2002}
David C, N\"{o}hammer B, Solak H, Ziegler E (2002) {Differential x-ray phase
  contrast imaging using a shearing interferometer}.
\newblock {\em Applied Physics Letters} 81:3287--3289.

\bibitem{Momose2003a}
Momose A et~al. (2003) {Demonstration of X-Ray Talbot Interferometry}.
\newblock {\em Japanese Journal of Applied Physics} 42:L866--L868.

\bibitem{Munro2012}
Munro P, Ignatyev K, Speller R, Olivo A (2012) {Phase and absorption retrieval
  using incoherent X-ray sources}.
\newblock {\em Proceedings of the National Academy of Sciences} 2012:2--7.

\bibitem{Pfeiffer2006}
Pfeiffer F, Weitkamp T, Bunk O, David C (2006) {Phase retrieval and
  differential phase-contrast imaging with low-brilliance X-ray sources}.
\newblock {\em Nature Physics} 2:258--261.

\bibitem{Nesch2009}
Nesch I et~al. (2009) {The design and application of an in-laboratory
  diffraction-enhanced x-ray imaging instrument.}
\newblock {\em The Review of scientific instruments} 80:093702.

\bibitem{Parham2009}
Parham C, Zhong Z, Connor DM, Chapman LD, Pisano ED (2009) {Design and
  Implementation of a Compact Low-Dose Diffraction Enhanced Medical Imaging
  System}.

\bibitem{Pfeiffer2008}
Pfeiffer F et~al. (2008) {Hard-X-ray dark-field imaging using a grating
  interferometer}.
\newblock {\em Nature Materials} 7:134--137.

\bibitem{Willner2013}
Willner M et~al. (2013) {Quantitative X-ray phase-contrast computed tomography
  at 82 keV}.
\newblock {\em Optics express} 21:4155--4166.

\bibitem{Donath2009}
Donath T et~al. (2009) {Inverse geometry for grating-based x-ray phase-contrast
  imaging}.
\newblock {\em Journal of Applied Physics} 106:054703.
